---
title: "Arima + Arima-Garch"
author: "Jiawei He"
date: "April 30, 2019"
output: html_document
---


```{r}
library(quantmod)
library(tseries)
library(forecast)

FB = getSymbols('FB', from='2010-01-01', to='2018-12-31',auto.assign = FALSE)
FB = na.omit(FB)
VZ = getSymbols('VZ', from='2010-01-01', to='2018-12-31',auto.assign = FALSE)
VZ = na.omit(VZ)
GOOGL = getSymbols('GOOGL', from='2010-01-01', to='2018-12-31',auto.assign = FALSE)
GOOGL = na.omit(GOOGL)
MSFT = getSymbols('MSFT', from='2010-01-01', to='2018-12-31',auto.assign = FALSE)
MSFT = na.omit(MSFT)

FB_prices = FB[,4]
VZ_prices = VZ[,4]
GOOGL_prices = GOOGL[,4]
MSFT_prices = MSFT[,4]

r_FB = diff(log(FB_prices),lag=1)
r_FB = r_FB[!is.na(r_FB)]
plot(r_FB, type='l', main='log returns plot of FB')

r_VZ = diff(log(VZ_prices),lag=1)
r_VZ = r_VZ[!is.na(r_VZ)]
plot(r_VZ, type='l', main='log returns plot of VZ')

r_GOOGL = diff(log(GOOGL_prices),lag=1)
r_GOOGL = r_GOOGL[!is.na(r_GOOGL)]
plot(r_GOOGL, type='l', main='log returns plot of GOOGL')

r_MSFT = diff(log(MSFT_prices),lag=1)
r_MSFT = r_MSFT[!is.na(r_MSFT)]
plot(r_MSFT, type='l', main='log returns plot of MSFT')

FB_test = getSymbols('FB', from='2019-01-01', to='2019-04-30',auto.assign = FALSE)
FB_test = na.omit(FB_test)
VZ_test = getSymbols('VZ', from='2019-01-01', to='2019-04-30',auto.assign = FALSE)
VZ_test = na.omit(VZ_test)
GOOGL_test = getSymbols('GOOGL', from='2019-01-01', to='2019-04-30',auto.assign = FALSE)
GOOGL_test = na.omit(GOOGL_test)
MSFT_test = getSymbols('MSFT', from='2019-01-01', to='2019-04-30',auto.assign = FALSE)
MSFT_test = na.omit(MSFT_test)

FB_test_prices = FB_test[,4]
VZ_test_prices = VZ_test[,4]
GOOGL_test_prices = GOOGL_test[,4]
MSFT_test_prices = MSFT_test[,4]

r_test_FB = diff(log(FB_test_prices),lag=1)
r_test_FB = r_test_FB[!is.na(r_test_FB)]
r_test_VZ = diff(log(VZ_test_prices),lag=1)
r_test_VZ = r_test_VZ[!is.na(r_test_VZ)]
r_test_GOOGL = diff(log(GOOGL_test_prices),lag=1)
r_test_GOOGL = r_test_GOOGL[!is.na(r_test_GOOGL)]
r_test_MSFT = diff(log(MSFT_test_prices),lag=1)
r_test_MSFT = r_test_MSFT[!is.na(r_test_MSFT)]

```


### Step 1: Test for Stationarity, Check autocorrelation and heteroscedasiticity
### we check if those data are stationary TS. We also check whether arima is enough. That is to say, we check the existance of heteroscedasticity.

### ADF检验：检验时间序列是否平稳: Performs the Augmented Dickey-Fuller test for the null hypothesis of a unit root of a univarate time series x (equivalently, x is a non-stationary time series).
### 结论：对于这四个TS，就算不做差分，也是平稳的，所以表白在后续分析中没有差分的必要性。
```{r}
# check stationary of three data sets
library(aTSA)
library(forecast)
cleaned_FB <- ts(r_FB)
cleaned_VZ <- ts(r_VZ)
cleaned_GOOGL <- ts(r_GOOGL)
cleaned_MSFT <- ts(r_MSFT)

adf.test(cleaned_FB)       # all < 0.05 
adf.test(cleaned_VZ)       # all < 0.05 
adf.test(cleaned_GOOGL) # all < 0.05
adf.test(cleaned_MSFT)   # all < 0.05
# < 0.05 means they are stationary time serise 拒绝了不平稳的原假设。

```

### If there is autocorrelation and heteroscedasiticity, it's absolutly not suitable to view the data as a random sample from some distribution.
### box-P 拒绝原假设则说明有自相关性，不能简单的视为random sample去fit一个distribution
### Breusch-Pagan 拒绝原假设说明有异方差

```{r}
# From box-p we know that all of them show autocorrelation
test_FB <- Box.test(cleaned_FB, lag = 1, type = c("Box-Pierce"), fitdf = 0)  # > 0.05 at lag1
test_VZ <- Box.test(cleaned_VZ, lag = 10, type = c("Box-Pierce"), fitdf = 0)  # lag > 10,  > 0.05 
test_GOOGL <- Box.test(cleaned_GOOGL, lag = 2, type = c("Box-Pierce"), fitdf = 0) # lag > 2,  > 0.05 
test_MSFT <- Box.test(cleaned_MSFT, lag = 1, type = c("Box-Pierce"), fitdf = 0) # > 0.05 at lag10
test_FB
test_VZ
test_GOOGL
test_MSFT



## !!!!!!!!!!!!!!!!!!! The test result show ARIMA is not enough  即为：其实存在着异方差的情况
library(lmtest)
bptest_FB <- bptest(y~x, studentize = TRUE, data = list(x=c(1:1663), y=cleaned_FB))        # < 0.05
bptest_VZ <- bptest(y~x, studentize = TRUE, data = list(x=c(1:2262), y=cleaned_VZ))        # > 0.05
bptest_GOOGL <- bptest(y~x, studentize = TRUE, data = list(x=c(1:2262), y=cleaned_GOOGL))  # > 0.05
bptest_MSFT <- bptest(y~x, studentize = TRUE, data = list(x=c(1:2262), y=cleaned_MSFT))    # > 0.05
bptest_FB
bptest_VZ
bptest_GOOGL
bptest_MSFT
```

#Diagnosing the ACF and PACF Plots
```{r}
par(mfrow=c(1,2))
acf(cleaned_FB, main="FB log-return", lag.max=100) ##autocorelation
pacf(cleaned_FB, main="FB log-return", lag.max=100) ##partial acf

par(mfrow=c(1,2))
acf(cleaned_VZ, main="VZ log-return")
pacf(cleaned_VZ, main="VZ log-return") 

par(mfrow=c(1,2))
acf(cleaned_GOOGL, main="GOOGL log-return")
pacf(cleaned_GOOGL,main="GOOGL log-return")

par(mfrow=c(1,2))
acf(cleaned_MSFT,main="MSFT log-return")
pacf(cleaned_MSFT,main="MSFT log-return") 

```


# fit a arima model for FB data
# 其实严格的来说，只有FB没有异方差，能用arima fit 其他都只能用arch或者garch
```{r}
library(quantmod);library(tseries);
library(timeSeries);library(forecast);library(xts)
TECHM = getSymbols('FB', from='2010-01-01', to='2019-04-28',auto.assign = FALSE)
TECHM = na.omit(TECHM)

stock_prices = TECHM[,4]

stock = diff(log(stock_prices),lag=1)
stock = stock[!is.na(stock)]

arima_FB <- auto.arima(stock, seasonal = TRUE, max.p = 10, max.q = 10, max.order = 10, ic = "aic",trace = T)
fit_FB <- arima(stock, order = c(2,0,2))
summary(fit_FB)

#forecast
breakpoint = floor(nrow(stock)*(2.865/3))
# Initialzing an xts object for Actual log returns
Actual_series = xts(0, as.Date("2014-11-25","%Y-%m-%d"))
 
# Initialzing a dataframe for the forecasted return series
forecasted_series = data.frame(Forecasted = numeric())

for (b in breakpoint:(nrow(stock)-1)) {
  stock_train = stock[1:b, ]
  stock_test = stock[(b+1):nrow(stock), ]
  
  # Summary of the ARIMA model using the determined (p,d,q) parameters
  fit = arima(stock_train, order = c(2, 0, 2), include.mean = FALSE)
  #summary(fit)
  
  # plotting a acf plot of the residuals
  #acf(fit$residuals,main="Residuals plot")
  
  # Forecasting the log returns
  arima.forecast = forecast(fit, h = 1, level=99)
  #summary(arima.forecast)
  
  # plotting the forecast
  #par(mfrow=c(1,1))
  #plot(arima.forecast, main = "ARIMA Forecast")
  
  # Creating a series of forecasted returns for the forecasted period
  forecasted_series = rbind(forecasted_series,arima.forecast$mean[1])
  colnames(forecasted_series) = c("Forecasted")
  
  # Creating a series of actual returns for the forecasted period
  Actual_return = stock[(b+1),]
  Actual_series = c(Actual_series,xts(Actual_return))
  rm(Actual_return)
  
  #print(stock_prices[(b+1),])
  #print(stock_prices[(b+2),])
}

# Adjust the length of the Actual return series
Actual_series = Actual_series[-1]

# Create a time series object of the forecasted series
forecasted_series = xts(forecasted_series,index(Actual_series))

# Create a plot of the two return series - Actual versus Forecasted
plot(Actual_series,type='l',main='Actual Returns Vs Forecasted Returns')
lines(forecasted_series,lwd=1.5,col='red')
legend('bottomright',c("Actual","Forecasted"),lty=c(1,1),lwd=c(1.5,1.5),col=c('black','red'))

# Create a table for the accuracy of the forecast
comparsion = merge(Actual_series,forecasted_series)
comparsion$Accuracy = sign(comparsion$Actual_series)==sign(comparsion$Forecasted)
print(comparsion)

# Compute the accuracy percentage metric
Accuracy_percentage = sum(comparsion$Accuracy == 1)*100/length(comparsion$Accuracy)
print(Accuracy_percentage)

acf(fit_FB$residuals)
pacf(fit_FB$residuals)
checkresiduals(fit_FB)
```



### fit arima-garch model for VZ, GOOGL and MSFT to do the prediction

```{r}
library(rugarch)

# fit VZ
arima_VZ <- auto.arima(cleaned_VZ, seasonal = TRUE,max.p = 10, max.q = 10, max.order = 10, ic = "aic",trace = T)

myspec_VZ<- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1), submodel = NULL, 
                                        external.regressors = NULL, variance.targeting = FALSE),
                  mean.model = list(armaOrder = c(2, 0), include.mean = TRUE, archm = FALSE, 
                                    archpow = 1, arfima = FALSE, external.regressors = NULL, 
                                    archex = FALSE),
                  distribution.model = "norm")

rVZ_fit <- ugarchfit(spec = myspec_VZ, data=r_VZ, solver="solnp")
rVZ_fit@fit$coef
rVZ_var <- rVZ_fit@fit$var
rVZ_res2 <- (rVZ_fit@fit$residuals)^2
plot(rVZ_res2, type = "l")
lines(rVZ_var, col = "green")
plot(rVZ_fit)

qqnorm(rVZ_fit@fit$residuals, main='Residuals(VZ)')
qqline(rVZ_fit@fit$residuals)
par(mfrow = c(1, 2))
acf(na.omit(rVZ_res2, main='ACF Squared Residuals(VZ)'))
pacf(na.omit(rVZ_res2, main='PACF Squared Residuals(VZ)'))

#forcast_method_1
total_VZ <- c(r_VZ, r_test_VZ)
VZ_windowLength = length(r_VZ)
VZ_foreLength = length(r_test_VZ)
VZ_forecasts <- vector(mode="character", length=VZ_foreLength)

# Model to compute the best ARIMA(p,d,q) model + GARCH(1,1)
for (d in 0:VZ_foreLength) {
  VZ_ReturnsOffset = total_VZ[(1+d):(VZ_windowLength+d)]
  
  # Fit the ARIMA model
  final.aic <- Inf
  final.order <- c(0,0,0)
  for (p in 0:5) for (q in 0:5) {
    if ( p == 0 && q == 0) {
      next
    }
    
    arimaFit = tryCatch(arima(VZ_ReturnsOffset, order=c(p, 0, q)), error=function(err) FALSE,
                         warning=function(err) FALSE)
    if(!is.logical(arimaFit)) {
      current.aic <- AIC(arimaFit)
      if (current.aic < final.aic) {
        final.aic <- current.aic
        final.order <- c(p, 0, q)
        final.arima <- arima(VZ_ReturnsOffset, order=final.order)
        }
      } else {
        next
      }
  }
  myspec = ugarchspec(variance.model=list(garchOrder=c(1,1)),
                    mean.model=list(armaOrder=c(final.order[1], final.order[3]), include.mean=T),
                    distribution.model="sged")   # skewed generalized error distribution
  
  VZ_fit = tryCatch(ugarchfit(myspec, VZ_ReturnsOffset, solver = 'hybrid'), 
                 error=function(e) e, warning=function(w) w)
  
  # If the GARCH model does not converge, set the direction to "long" else
  # choose the correct forecast direction based on the returns prediction
  # Output the results to the screen and the forecasts vector
      
  if(is(VZ_fit, "warning")) {
      VZ_forecasts[d+1] = paste(index(VZ_ReturnsOffset[VZ_windowLength]), 1, sep=",")
      print(paste(index(VZ_ReturnsOffset[VZ_windowLength]), 1, sep=","))
    } else {
      VZ_fore = ugarchforecast(VZ_fit, n.ahead=1)
      ind = VZ_fore@forecast$seriesFor
      VZ_forecasts[d+1] = ind[1]
      print(VZ_forecasts[d+1])
    }
}
#write.csv(VZ_forecasts, file="VZ_forecastscsv", row.names=FALSE)

plot(as.matrix(r_test_VZ), type = "l", ylab = "log return of VZ")
lines(1:length(VZ_forecasts), VZ_forecasts, col = "green")

#forecast_method_2
#rVZ_fore <- ugarchforecast(rVZ_fit, n.ahead = length(r_test_VZ))
#plot(as.matrix(r_test_VZ), type = "l")
#lines(1:length(rVZ_fore@forecast$seriesFor), rVZ_fore@forecast$seriesFor, col = "green")

# fit googl

arima_GOOGL <- auto.arima(cleaned_GOOGL, seasonal = TRUE,max.p = 10, max.q = 10, max.order = 10, ic = "aic",trace = T)

myspec_GOOGL<- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1), submodel = NULL, 
                                        external.regressors = NULL, variance.targeting = FALSE),
                  mean.model = list(armaOrder = c(0, 0), include.mean = TRUE, archm = FALSE, 
                                    archpow = 1, arfima = FALSE, external.regressors = NULL, 
                                    archex = FALSE),
                  distribution.model = "norm")

rGOOGL_fit <- ugarchfit(spec = myspec_GOOGL, data=r_GOOGL, solver="solnp")
rGOOGL_fit@fit$coef
rGOOGL_var <- rGOOGL_fit@fit$var
rGOOGL_res2 <- (rGOOGL_fit@fit$residuals)^2
plot(rGOOGL_res2, type = "l")
lines(rGOOGL_var, col = "green")
plot(rGOOGL_fit)



# fit_msft
arima_MSFT <- auto.arima(cleaned_MSFT, seasonal = TRUE,max.p = 10, max.q = 10, max.order = 10, ic = "aic",trace = T)

myspec_MSFT<- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1), submodel = NULL, 
                                        external.regressors = NULL, variance.targeting = FALSE),
                  mean.model = list(armaOrder = c(1, 1), include.mean = TRUE, archm = FALSE, 
                                    archpow = 1, arfima = FALSE, external.regressors = NULL, 
                                    archex = FALSE),
                  distribution.model = "norm")


rMSFT_fit <- ugarchfit(spec = myspec_MSFT,data=r_MSFT, solver="solnp")
rMSFT_fit@fit$coef
rMSFT_var <- rMSFT_fit@fit$var
rMSFT_res2 <- (rMSFT_fit@fit$residuals)^2
plot(rMSFT_res2, type = "l")
lines(rMSFT_var, col = "green")
plot(rMSFT_fit)


```